### 2017-03-02 Lab_2/solutions/L2-5-1.tex
Modified some L2 answers, cleaned up the L2 traces. Apart from 2-5-2 L2 is roughly finished
Former-commit-id: e23d15b4d046db2d1a7efe0d385cd2063bea80e3 [formerly 667ac0bcf380efc65a8adcd7028db2ed790746ce [formerly 667ac0bcf380efc65a8adcd7028db2ed790746ce [formerly 147b063b2b4b0cc6af7827f13c3c03686ff0b711]]]
Former-commit-id: 9335664ea7e24b951bcf88594bcb3acc14c11ada
Former-commit-id: 0880c005726e10a7200c71b6dd62eef2a777fe49
Former-commit-id: 2e53566381fd089a1354c56a8389e71d68277fe5

For this exercise, we will be comparing packet 2 from traces/L2-4-1.36.pcap and packet 2 from traces/L2-5-1.STA1.pcap.
For the purpose of comparing the WLAN management frames, I have included them below:

@@

for the beacon frame captured in exercise 5:

@@

A first difference we observed is that the capabilities information beacon frame captured
in exercise 5 contains different capabilities information than the one captured in exercise 4:
the ex5 beacon frame shows that the sender of the beacon frame is a STA and that the network is
an ad-hoc network, while in exercise 4 the capabilities reflect that the transmitter is an AP
and the network is not ad-hoc.\\
For the tagged parameters section, the ex5 beacon is bigger. It contains some IBSS parameters (ATIM) and vendor specifici information about the ad-hoc network.
 In the ex4 beacon, the tagged parameters contain information about the channel and the Traffic Indication Map.

>>>>

For this exercise, we will be comparing packet 2 from traces/L2-4-1.36.pcap and packet 2 from traces/L2-5-1.STA1.pcap.
They are included below for convenience:

@@

For the beacon frame captured in exercise 5:

@@

A first difference we observed is in the capabilities information parameters:
the ad-hoc beacon frame shows that the sender of the beacon frame is a STA and that the network is
an ad-hoc network, while the AP's capabilities reflect that the transmitter is an AP
and the network is not in an IBSS (i.e. not ad-hoc).\\
For the tagged parameters section, the two contain different parameter sets, making the ad-hoc one 4 bytes longer. The ad-hoc frame contains an IBSS parameter set with the Announcement Traffic Indication Message (ATIM) window and vendor specificic information parameters concerning Quality of Service.
 In the AP beacon, the tagged parameter sets contain information about the channel and the Traffic Indication Map.
